Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex

\section{Related Works}
\subsection{Whitened Histograms of Orientations (WHO)}
% History of Whitening and how whitening works
Recently, Hariharan \emph{et al.} introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative. Whitening is a common signal processing operation for decorrelating a set of random variables \cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we remove 2nd order correlation between all features. So, all elements in the random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots, \tilde{X}_k\right]$, become more independent. In the context of HOG features, a whitened HOG template will produce Gaussian noise when convolved with a random natural image, but a delta-like response on an image matching the template. WHO templates are more discriminative than standard HOG templates because they only capture the gradients that differentiate the object from random images.

>>>>

\section{Related Works}
\subsection{Whitened Histograms of Orientations (WHO)}
% History of Whitening and how whitening works
Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative. Whitening is a common signal processing operation for decorrelating a set of random variables \cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we remove 2nd order correlation between all features. So, all elements in the random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots, \tilde{X}_k\right]$, become more independent. In the context of HOG features, a whitened HOG template will produce Gaussian noise when convolved with a random natural image, but a delta-like response on an image matching the template. WHO templates are more discriminative than standard HOG templates because they only capture the gradients that differentiate the object from random images.
